---
title: "HW1"
author: Yi Sun
output: github_document
---

Solution to HW1.

```{r setup, include = FALSE}
library(tidyverse)
```

# Problem 1

Create a data frame comprised of specified elements.

```{r prob1_data_frame}
prob1_df = 
  tibble(
    samp = rnorm(10),
    samp_gt_0 = samp > 0,
    char_leng_10 = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
    factor_3_lvl = factor(c("high", "high", "high", "high", "mod", "mod", "mod", "low", "low", "low"))
)
```

Try to take the mean of each variable in the data frame.

```{r prob1_mean}
mean(pull(prob1_df, samp))
mean(pull(prob1_df, samp_gt_0))
mean(pull(prob1_df, char_leng_10))
mean(pull(prob1_df, factor_3_lvl))
```

I can only take the mean of numeric or logical variables but not character or factor variables.

Try to convert the logical variable `samp_gt_0`, character variable `char_leng_10`, and factor variable `factor_3_lvl` into numeric variables.

```{r prob1_convert, eval=FALSE}
as.numeric(pull(prob1_df, samp_gt_0))
as.numeric(pull(prob1_df, char_leng_10))
as.numeric(pull(prob1_df, factor_3_lvl))
```

The logical variable `samp_gt_0` and factor variable `factor_3_lvl` are converted into numeric variables, but I cannot convert the character variable `char_leng_10` into a numeric variable (returning NAs). I think it's because there are characters included in the string values of `char_leng_10` (i.e., string values like "111", "222", "333" of a character variable can be converted into numeric values).

This may help explain why I can only take the mean of numeric or logical variables: values of factor variables are not numbers before factor variables are converted into numeric variables, and values of logical variables are interpreted as 1 for TRUE and 0 for FALSE when I take the mean. String values of character variables including characters are not numbers and even cannot be converted into numeric values.

Try to multiply the numeric variable `samp` by the results of different conversions on the logical variable `samp_gt_0`.

```{r prob1_multiply}
as.numeric(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)
as.factor(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)
as.numeric(as.factor(pull(prob1_df, samp_gt_0))) * pull(prob1_df, samp)
```

`as.factor` function can convert logical variables into factor variables, but the result of conversion cannot directly multiply numeric variables. I can only multiply numeric variables by numeric variables.

# Problem 2

The summary of the `penguins` dataset is as below:

```{r prob2_data_summary}
data("penguins", package = "palmerpenguins")
summary(penguins)
```

This dataset has `r nrow(penguins)` rows and `r ncol(penguins)` columns.

The mean flipper length is `r mean(pull(penguins, flipper_length_mm), na.rm = TRUE)` mm.

Make a scatterplot of `flipper_length_mm` (y) vs `bill_length_mm` (x) and color points using the `species` variable.

```{r prob2_scatterplot}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()
ggsave(file = "hw1_prob2_scatterplot.png")
```

The scatterplot is saved as "hw1_prob2_scatterplot.png".