---
title: "hw1"
author: Yi Sun
output: github_document
---

Solution to hw1.

```{r, include = FALSE}
library(tidyverse)
```

# Problem 1

Create a data frame comprised of specified elements.

```{r}
prob1_df = 
  tibble(
    samp = rnorm(10),
    samp_gt_0 = samp > 0,
    char_leng_10 = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
    factor_3_lvl = factor(c("high", "high", "high", "high", "mod", "mod", "mod", "low", "low", "low"))
)
```

Try to take the mean of each variable in the data frame.

```{r}
mean(pull(prob1_df, samp))
mean(pull(prob1_df, samp_gt_0))
mean(pull(prob1_df, char_leng_10))
mean(pull(prob1_df, factor_3_lvl))
```

I can only take the mean of numeric or logical variables but not character or factor variables.

```{r, eval = FALSE}
as.numeric(pull(prob1_df, samp_gt_0))
as.numeric(pull(prob1_df, char_leng_10))
as.numeric(pull(prob1_df, factor_3_lvl))
```

Logical and factor variables are converted to numeric variables, but I cannot convert character variables to numeric variables. I think it's because character variables don't have an order and the letters are all "equal." 

This may help explain why I can only take the mean of numeric or logical variables: factor variables are not numbers before being converted to numeric variables, and logical variables are interpreted as "1" for "yes" and "0" for "no" when I take the mean. Character variables are not numbers and even cannot be converted to numeric variables.

```{r}
as.numeric(pull(prob1_df, samp_gt_0))*pull(prob1_df, samp)
as.factor(pull(prob1_df, samp_gt_0))*pull(prob1_df, samp)
as.numeric(as.factor(pull(prob1_df, samp_gt_0)))*pull(prob1_df, samp)
```

# Problem 2
